A tutorial on how to do the same thing more than once

### 2021-08-06 manuscript.Rmd
move this discussion to the footnote closes #192

[^caution-mww]: The Mann–Whitney–Wilcoxon is in fact **not** more robust than the Welch corrected t-test for reasonably large sample sizes. The interested reader can use the [provided code for the simulation](https://github.com/aaronpeikert/repro-tutorial/blob/main/simulation.R) to verify that the t-test provides unbiased effect sizes but the Mann–Whitney–Wilcoxon overestimates effect size with increasing sample size and skewness.

@@

The t-test and Mann–Whitney–Wilcoxon test are arguably the most often used hypothesis test [@fagerlandTtestsNonparametricTests2012; @hortonStatisticalMethodsJournal2005 reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005].
The analytical strategy presented here is, in fact, suboptimal concerning several criteria (untested assumption of measurement invariance [@putnickMeasurementInvarianceConventions2016], underestimation of effect size in the presence of measurement error [@frostCorrectingRegressionDilution2000], overestimation of effect size for highly skewed distributions [@stonehouseRobustnessTestsCombined1998]).

>>>>

[^caution-mww]: The t-test and Mann–Whitney–Wilcoxon test are arguably the most often used hypothesis test [@fagerlandTtestsNonparametricTests2012; @hortonStatisticalMethodsJournal2005 reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005].
The analytical strategy presented here is, in fact, suboptimal concerning several criteria (untested assumption of measurement invariance [@putnickMeasurementInvarianceConventions2016], underestimation of effect size in the presence of measurement error [@frostCorrectingRegressionDilution2000], overestimation of effect size for highly skewed distributions [@stonehouseRobustnessTestsCombined1998]). The interested reader can use the [provided code for the simulation](https://github.com/aaronpeikert/repro-tutorial/blob/main/simulation.R) to verify that the t-test provides unbiased effect sizes but the Mann–Whitney–Wilcoxon overestimates effect size with increasing sample size and skewness.

@@
